A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-09-14 04_Severity_MetaAnalysis.Rmd
Grammar

   - *Powdery mildew severity* the response variable (1-9 scale)

@@

   - *spray_management* a moderator to evaluate the difference in effect size attributed to fungicide application timing.

   - *id* random variable indicating each treatment is independent

<br>

Load libraries and data  
```{r MEsummary_Libraries2, echo=TRUE,results='hide'}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               kableExtra,
               RColorBrewer,
               metafor,
               here,
               netmeta,
               multcomp,
               dplyr,
               flextable,
               gam,
               clubSandwich)

>>>>

   - *Powdery mildew severity*, the response variable (1-9 scale)

@@

   - *spray_management*, a moderator to evaluate the difference in effect size attributed to fungicide application timing.

   - *id*, random variable indicating each treatment is independent

Load libraries and data.

```{r MEsummary_Libraries2, echo=TRUE,results='hide'}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               kableExtra,
               RColorBrewer,
               metafor,
               here,
               netmeta,
               multcomp,
               dplyr,
               flextable,
               gam,
               clubSandwich)
